Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-02 paper.tex
fadded to motivationsection in Intro

%{Motivation: Why bother re-engineering a formal specification for a nicely developed privacy oriented app? physical aspects (adoption rate), formal proof etc}
The technical advantage of modeling an application in the Isabelle Insider framework lies
in (a) having explicit representations of infrastructures, actors and policies in a
formal model that (b) allows additional automated verification of security properties
within the interactive theorem prover Isabelle.
Although the Corona-virus app hass been produced based on a sophisticated security
concept conceived by experts in the field, to our knowledge, no formal verification
has been involved.

>>>>

%{Motivation: Why bother re-engineering a formal specification for a nicely developed privacy oriented app? physical aspects (adoption rate), formal proof etc}
The technical advantage of modeling an application in the Isabelle Insider framework lies
in (a) having explicit representations of infrastructures, actors and policies in a
formal model that (b) allows additional automated verification of security properties
within the interactive theorem prover Isabelle.
Although the Corona-virus app has been produced based on a sophisticated security
concept conceived by experts in the field, to our knowledge, no formal verification
has been involved. Even if a ``post-production'' formal specification seems pointless,
it allows to reveal weak points of the architecture, show that the measures that have
been conceived are suitable to cover those weak points. Thereby, we believe
that our current work is useful to increase the trust in the Corona-virus app necessary for
its wide adoption which in turn is crucial for it to be efficient.
